### 2017-07-05 README.Rmd
package dev

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# WetlandComparison

The goal of WetlandComparison is to ...

## Installation

You can install WetlandComparison from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("samdchamberlain/WetlandComparison")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```

### 2017-07-05 R/WetlandComparison-package.r

@@ -1,0 +1,5 @@
+#' WetlandComparison.
+#'
+#' @name WetlandComparison
+#' @docType package
+NULL

### 2017-07-05 tests/testthat.R

@@ -1,0 +1,4 @@
+library(testthat)
+library(WetlandComparison)
+
+test_check("WetlandComparison")

### 2017-07-05 README.Rmd
update ReadMe
Change to basic .yaml and add to Readme

@@
 <!-- README.md is generated from README.Rmd. Please edit that file -->
+
+[![Travis-CI Build Status](https://travis-ci.org/samdchamberlain/WetlandComparison.svg?branch=master)](https://travis-ci.org/samdchamberlain/WetlandComparison)
 
@@
 
-The goal of WetlandComparison is to ...
+The goal of WetlandComparison is to make a first attempt at a reproducible research R package. This will still be somewhat hampered by the fact that much of this research is conducted with Matlab.
 

### 2017-07-05 R/alluvium_processing.R
All processing the knitting for the day. Finally, got source files running and working markdown file in a true package format. Still need testing, but otherwise well on the way to reproducible example

@@ -1,0 +1,83 @@
+# Script to load, merge, and process daily to annual budgets.
+# Code varies for each site as input met variables vary across sites
+# Site: Alluvium
+
+# load datasets
+load("../data/alluvium_eddy.Rda") #eddy fluxes
+load("../data/alluvium_met.Rda") #met variables
+
+# merge met and eddy dataframes by shared time variable
+alluvium_all <- merge(alluvium_eddy, alluvium_met, by="decday")
+alluvium_all$datetime <- as.POSIXct((alluvium_all$Mdate  - 719529)*86400, origin = "1970-01-01", tz = "UTC")
+alluvium_all$month <- month(alluvium_all$datetime)
+alluvium_all$yr.m <- paste(alluvium_all$year, alluvium_all$month, sep="_")
+alluvium_all$dday <- floor(alluvium_all$decday)
+
+# create a long-term water temperature measure, as the probes have changed over time
+# when we don't have a 10cm water temp measurement, add 8cm depth in place
+alluvium_all$TW_10cm <- ifelse(is.na(alluvium_all$TW_10cm), alluvium_all$TW_8cm, alluvium_all$TW_10cm)
+alluvium_all$TW_10cm <- na.approx(alluvium_all$TW_10cm, na.rm=F) # linear interpolate holes
+
+#Simple average of daily fluxes for pre-gapfilled values
+daily <- alluvium_all %>%
+  group_by(dday) %>%
+  summarise(mNEE = mean(wc_gf),         #NEE (umol m-2 s-1)
+            c_obs = sum(!is.na(wc)),    #num of non-filled observations (applies all _obs)
+            mCH4 = mean(wm_gf),         #CH4 flux (nmol m-2 s-1)
+            m_obs = sum(!is.na(wm)),
+            GPP = mean(gpp_ANNnight),   #partitioned GPP (umol m-2 s-1)
+            ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
+            ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
+            q_obs = sum(!is.na(wq)),
+            H = mean(H_gf),                    #sensible heat flux (W m-2)
+            mGCC = mean(GCC, na.rm=T),         #green index
[…]

### 2017-07-05 R/peat19_processing.R

@@ -1,0 +1,73 @@
+# Script to load, merge, and process daily to annual budgets.
+# Code varies for each site as input met variables vary across sites
+# Site: Peat 19 yr old
+
+# load datasets
+load("../data/peat19_eddy.Rda") #eddy fluxes
+load("../data/peat19_met.Rda") #met variables
+
+# merge met and eddy dataframes by shared time variable
+peat19_all <- merge(peat19_eddy, peat19_met, by="decday")
+peat19_all$datetime <- as.POSIXct((peat19_all$Mdate  - 719529)*86400, origin = "1970-01-01", tz = "UTC")
+peat19_all$month <- month(peat19_all$datetime)
+peat19_all$yr.m <- paste(peat19_all$year, peat19_all$month, sep="_")
+peat19_all$dday <- floor(peat19_all$decday)
+
+#Simple average of daily fluxes for gapfilled values
+daily <- peat19_all %>%
+  group_by(dday) %>%
+  summarise(mNEE = mean(wc_gf),         #NEE (umol m-2 s-1)
+            c_obs = sum(!is.na(wc)),    #num of non-filled observations (applies all _obs)
+            mCH4 = mean(wm_gf),         #CH4 flux (nmol m-2 s-1)
+            m_obs = sum(!is.na(wm)),
+            GPP = mean(gpp_ANNnight),   #partitioned GPP (umol m-2 s-1)
+            ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
+            ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
+            q_obs = sum(!is.na(wq)),
+            H = mean(H_gf),             #sensible heat flux (W m-2)
+            mGCC = mean(GCC, na.rm=T),  #green index
+            PAR = mean(PAR, na.rm=T),   #photosynthetic active radiation (umol m-2 s-1)
+            Tair = mean(TA.y, na.rm=T), #air temp (deg C)
+            Tw = mean(TW_8cm, na.rm=T), #water temp (deg C)
+            Ts = mean(TS_8cm, na.rm=T), #soil temp (deg C)
+            mVPD = mean(VPD, na.rm=T),  #VPD (kPa)
+            PA = mean(PA.y, na.rm=T),   #atm pressure (kPa)
[…]

### 2017-07-05 R/peat6_processing.R

@@ -1,0 +1,73 @@
+# Script to load, merge, and process daily to annual budgets.
+# Code varies for each site as input met variables vary across sites
+# Site: Peat 6 yr old
+
+# load datasets
+load("../data/peat6_eddy.Rda") #eddy fluxes
+load("../data/peat6_met.Rda") #met variables
+
+# merge met and eddy dataframes by shared time variable
+peat6_all <- merge(peat6_eddy, peat6_met, by="decday")
+peat6_all$datetime <- as.POSIXct((peat6_all$Mdate  - 719529)*86400, origin = "1970-01-01", tz = "UTC")
+peat6_all$month <- month(peat6_all$datetime)
+peat6_all$yr.m <- paste(peat6_all$year, peat6_all$month, sep="_")
+peat6_all$dday <- floor(peat6_all$decday)
+
+#Simple average of daily fluxes for gapfilled values
+daily <- peat6_all %>%
+  group_by(dday) %>%
+  summarise(mNEE = mean(wc_gf),         #NEE (umol m-2 s-1)
+            c_obs = sum(!is.na(wc)),    #num of non-filled observations (applies all _obs)
+            mCH4 = mean(wm_gf),         #CH4 flux (nmol m-2 s-1)
+            m_obs = sum(!is.na(wm)),
+            GPP = mean(gpp_ANNnight),   #partitioned GPP (umol m-2 s-1)
+            ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
+            ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
+            q_obs = sum(!is.na(wq)),
+            H = mean(H_gf),                    #sensible heat flux (W m-2)
+            mGCC = mean(GCCsmooth, na.rm=T),   #green index
+            PAR = mean(PAR, na.rm=T),          #photosynthetic active radiation (umol m-2 s-1)
+            Tair = mean(TA.y, na.rm=T),        #air temp (deg C)
+            Tw = mean(TW_WATER_10cm, na.rm=T), #water temp (deg C)
+            Ts = mean(TS_TULE_8cm, na.rm=T),   #soil temp (deg C)
+            mVPD = mean(VPD, na.rm=T),         #VPD (kPa)
+            PA = mean(PA.y, na.rm=T),          #atm pressure (kPa)
[…]

### 2017-07-05 tests/testthat/test_something.R
try a real test??

@@ -1,0 +1,6 @@
+library("knitr")
+#knit(system.file("vignettes", "intro.Rmd", package="WetlandComparison"))
+#knit(system.file("vignettes", "full_analysis.Rmd", package="WetlandComparison"))
+## No "Error" should appear
+#expect_equal(length(grep("Error", readLines("intro.html"))), 0)
+#expect_equal(length(grep("Error", readLines("full_analysis.html"))), 0)

### 2017-07-06 R/alluvium_processing.R
Wow, I think I finally got a working package.

@@ -1,10 +1,15 @@
-# Script to load, merge, and process daily to annual budgets.
-# Code varies for each site as input met variables vary across sites
-# Site: Alluvium
+#' Script to load, merge, and process daily to annual budgets.
+#' Code varies for each site as input met variables vary across sites
+#' Site: Alluvium
+#'
+#' @import dplyr
+#' @importFrom dplyr "%>%"
+#' @importFrom lubridate month
+#' @importFrom zoo na.approx
 
 # load datasets
-load("../data/alluvium_eddy.Rda") #eddy fluxes
-load("../data/alluvium_met.Rda") #met variables
+load("data/alluvium_eddy.Rda") #eddy fluxes
+load("data/alluvium_met.Rda") #met variables
 
 # merge met and eddy dataframes by shared time variable
 alluvium_all <- merge(alluvium_eddy, alluvium_met, by="decday")

### 2017-07-06 R/peat19_processing.R

@@ -1,10 +1,14 @@
-# Script to load, merge, and process daily to annual budgets.
-# Code varies for each site as input met variables vary across sites
-# Site: Peat 19 yr old
+#' Script to load, merge, and process daily to annual budgets.
+#' Code varies for each site as input met variables vary across sites
+#' Site: Peat 19 yr old
+#'
+#' @import dplyr
+#' @importFrom dplyr "%>%"
+#' @importFrom lubridate month
 
 # load datasets
-load("../data/peat19_eddy.Rda") #eddy fluxes
-load("../data/peat19_met.Rda") #met variables
+load("data/peat19_eddy.Rda") #eddy fluxes
+load("data/peat19_met.Rda") #met variables
 
 # merge met and eddy dataframes by shared time variable
 peat19_all <- merge(peat19_eddy, peat19_met, by="decday")

### 2017-07-06 R/peat6_processing.R

@@ -1,10 +1,15 @@
-# Script to load, merge, and process daily to annual budgets.
-# Code varies for each site as input met variables vary across sites
-# Site: Peat 6 yr old
+#' Script to load, merge, and process daily to annual budgets.
+#' Code varies for each site as input met variables vary across sites
+#' Site: Peat 6 yr old
+#'
+#' @import dplyr
+#' @importFrom dplyr "%>%"
+#' @importFrom lubridate month
+
 
 # load datasets
-load("../data/peat6_eddy.Rda") #eddy fluxes
-load("../data/peat6_met.Rda") #met variables
+load("data/peat6_eddy.Rda") #eddy fluxes
+load("data/peat6_met.Rda") #met variables
 
 # merge met and eddy dataframes by shared time variable
 peat6_all <- merge(peat6_eddy, peat6_met, by="decday")

### 2017-07-11 R/Diel_patterns.R
Many updates with new processing scripts

@@ -1,0 +1,64 @@
+#' Script to calculate diel flux patterns across three core wetland sites
+#'
+#' Sites: Peat 7 yr old, Peat 20 yr old, Alluvium 4 yr old
+#'
+#' @import dplyr
+#' @importFrom dplyr "%>%"
+#' @importFrom lubridate month
+
+## Process each core site into diel values then we will merge them into a single file for visualization
+# diel fluxes from 6yr old peat site
+diel_peat6 <- peat6_all %>%
+  subset(DOY < 301 & DOY > 99 & year > 2010) %>% #use growing season only with full data years
+  group_by(year, time, site) %>%
+  summarise(CH4 = mean(wm, na.rm=T),
+            sdCH4 = sd(wm, na.rm=T),
+            GPP = mean(wc, na.rm=T),
+            sdGPP = sd(wc, na.rm=T),
+            ET = mean(wq, na.rm=T),
+            sdET = sd(wq, na.rm=T),
+            Ta = mean(TA.y, na.rm=T),
+            sdTa = sd(TA.y, na.rm=T),
+            Tw = mean(TW_TULE_10cm, na.rm=T),
+            sdTw = sd(TW_TULE_10cm, na.rm=T),
+            PAR = mean(PAR, na.rm=T),
+            sdPAR = sd(PAR, na.rm=T))
+
+#diel fluxes for 19yr old peat site
+diel_peat19 <- peat19_all %>%
+  subset(DOY.x < 301 & DOY.x > 99) %>% #use growing season only
+  group_by(year, time, site) %>%
+  summarise(CH4 = mean(wm, na.rm=T),
+            sdCH4 = sd(wm, na.rm=T),
+            GPP = mean(wc, na.rm=T),
+            sdGPP = sd(wc, na.rm=T),
+            ET = mean(wq, na.rm=T),
+            sdET = sd(wq, na.rm=T),
+            Ta = mean(TA.y, na.rm=T),
+            sdTa = sd(TA.y, na.rm=T),
+            Tw = mean(TW_8cm, na.rm=T),
+            sdTw = sd(TW_8cm, na.rm=T),
+            PAR = mean(PAR, na.rm=T),
+            sdPAR = sd(PAR, na.rm=T))
+
+#diel fluxes for 4yr old alluvium site
+diel_alluvium <- alluvium_all %>%
+  subset(DOY.x < 301 & DOY.x > 99) %>% #use growing season only
[…]

### 2017-07-11 R/alluvium_processing.R

@@ -78,6 +78,7 @@ alluvium_yearly <- yearly
 alluvium_daily <- daily
 alluvium_yearly$site <- "Alluvium - 3 yr old"
 alluvium_daily$site <- "Alluvium - 3 yr old"
+alluvium_all$site <- "Alluvium - 3 yr old"
 
 #remove other dataframes
 rm(yearly); rm(daily); rm(alluvium_eddy); rm(alluvium_met)

### 2017-07-11 R/peat19_processing.R

@@ -72,6 +72,7 @@ peat19_yearly <- yearly
 peat19_daily <- daily
 peat19_yearly$site <- "Peat - 19 yr old"
 peat19_daily$site <- "Peat - 19 yr old"
+peat19_all$site <- "Peat - 19 yr old"
 
 #remove other dataframes
 rm(yearly); rm(daily); rm(peat19_eddy); rm(peat19_met)

### 2017-07-11 R/peat6_processing.R

@@ -73,6 +73,7 @@ peat6_yearly <- yearly
 peat6_daily <- daily
 peat6_yearly$site <- "Peat - 6 yr old"
 peat6_daily$site <- "Peat - 6 yr old"
+peat6_all$site <- "Peat - 6 yr old"
 
 #remove other dataframes
 rm(yearly); rm(daily); rm(peat6_eddy); rm(peat6_met)

### 2017-07-11 R/soils.R

@@ -1,0 +1,40 @@
+#' Script to process soils data across sites
+#'
+#' Sites: Peat 20 yr old, Alluvium 4 yr old. More to follow
+#'
+#' @import dplyr
+#' @importFrom readr read_csv
+#' @importFrom dplyr "%>%"
+
+#load data.frames for pH and iron
+pH_data <- read_csv("data/pH.csv")
+Fe_data <- read_csv("data/Fe_data.csv")
+
+#clean data tables to remove empty columns and rows
+pH_data <- pH_data[,colSums(is.na(pH_data))<nrow(pH_data)] #columns
+pH_data <- na.omit(pH_data) #rows
+
+Fe_data <- Fe_data[,colSums(is.na(Fe_data))<nrow(Fe_data)] #columns
+Fe_data <- na.omit(Fe_data) #rows
+
+#merge data sources to single dataframe, clean up remaining dataframe
+soils_df <- merge(pH_data, Fe_data, by="Number") %>%
+  select(Number, `Depth (cm).x`, Tract.x, Point.x, Area.x, pH, `Fe(II)_mg.g`,
+         Fe_all_mg.g, `Fe(III)_mg.g`) %>%
+  rename(Depth = `Depth (cm).x`, FeII_mg.g = `Fe(II)_mg.g`, FeIII_mg.g = `Fe(III)_mg.g`)
+
+#create site variable based on 'Area' site names
+soils_df$site <- ifelse(soils_df$Area.x == "East End", "Alluvium - 3 yr old",
+                        "Peat - 19 yr old")
+
+#What percent of iron is in oxidized form?
+soils_df$percent_ox <- (soils_df$FeIII_mg.g/soils_df$Fe_all_mg.g)*100
+soils_df$percent_ox <- ifelse(soils_df$FeIII_mg.g < 0, 0, soils_df$percent_ox) #if FeIII is less than zero set to zero
+
+#New surface v. deep column represents more accurately that we are comparing a recent muck layer
+# to a deep older soil layer. This deep layer at the peat site is actually ~0.7m below surface
+soils_df$horizon <- ifelse(soils_df$Depth == "0-15", "surface", "deep")
+
+#Also, need to fix West Pond point 1 where 15-30 was also 'surface' litter
+soils_df$horizon <- ifelse(soils_df$Area.x == "West Pond" & soils_df$Point.x == "P1",
+                           "surface", soils_df$horizon)

### 2017-07-12 R/alluvium_processing.R
Updated processing to full_analysis and fix TRAVIS push problems

@@ -4,19 +4,10 @@
 #'
 #' @import dplyr
 #' @importFrom dplyr "%>%"
-#' @importFrom lubridate month
 #' @importFrom zoo na.approx
 
-# load datasets
-load("data/alluvium_eddy.Rda") #eddy fluxes
-load("data/alluvium_met.Rda") #met variables
-
-# merge met and eddy dataframes by shared time variable
-alluvium_all <- merge(alluvium_eddy, alluvium_met, by="decday")
-alluvium_all$datetime <- as.POSIXct((alluvium_all$Mdate  - 719529)*86400, origin = "1970-01-01", tz = "UTC")
-alluvium_all$month <- month(alluvium_all$datetime)
-alluvium_all$yr.m <- paste(alluvium_all$year, alluvium_all$month, sep="_")
-alluvium_all$dday <- floor(alluvium_all$decday)
+# load eddy flux and met dataset
+load("data/alluvium_all.Rda")
 
 # create a long-term water temperature measure, as the probes have changed over time
 # when we don't have a 10cm water temp measurement, add 8cm depth in place
@@ -81,7 +72,7 @@ alluvium_daily$site <- "Alluvium - 3 yr old"
 alluvium_all$site <- "Alluvium - 3 yr old"
 
 #remove other dataframes
-rm(yearly); rm(daily); rm(alluvium_eddy); rm(alluvium_met)
+rm(yearly); rm(daily);
 
 
 

### 2017-07-12 R/peat19_processing.R

@@ -4,18 +4,9 @@
 #'
 #' @import dplyr
 #' @importFrom dplyr "%>%"
-#' @importFrom lubridate month
 
-# load datasets
-load("data/peat19_eddy.Rda") #eddy fluxes
-load("data/peat19_met.Rda") #met variables
-
-# merge met and eddy dataframes by shared time variable
-peat19_all <- merge(peat19_eddy, peat19_met, by="decday")
-peat19_all$datetime <- as.POSIXct((peat19_all$Mdate  - 719529)*86400, origin = "1970-01-01", tz = "UTC")
-peat19_all$month <- month(peat19_all$datetime)
-peat19_all$yr.m <- paste(peat19_all$year, peat19_all$month, sep="_")
-peat19_all$dday <- floor(peat19_all$decday)
+# load eddy flux and met dataset
+load("data/peat19_all.Rda")
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat19_all %>%
@@ -75,4 +66,4 @@ peat19_daily$site <- "Peat - 19 yr old"
 peat19_all$site <- "Peat - 19 yr old"
 
 #remove other dataframes
-rm(yearly); rm(daily); rm(peat19_eddy); rm(peat19_met)
+rm(yearly); rm(daily);

### 2017-07-12 R/peat6_processing.R

@@ -4,19 +4,9 @@
 #'
 #' @import dplyr
 #' @importFrom dplyr "%>%"
-#' @importFrom lubridate month
 
-
-# load datasets
-load("data/peat6_eddy.Rda") #eddy fluxes
-load("data/peat6_met.Rda") #met variables
-
-# merge met and eddy dataframes by shared time variable
-peat6_all <- merge(peat6_eddy, peat6_met, by="decday")
-peat6_all$datetime <- as.POSIXct((peat6_all$Mdate  - 719529)*86400, origin = "1970-01-01", tz = "UTC")
-peat6_all$month <- month(peat6_all$datetime)
-peat6_all$yr.m <- paste(peat6_all$year, peat6_all$month, sep="_")
-peat6_all$dday <- floor(peat6_all$decday)
+# load eddy flux and met dataset
+load("data/peat6_all.Rda")
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat6_all %>%
@@ -76,4 +66,4 @@ peat6_daily$site <- "Peat - 6 yr old"
 peat6_all$site <- "Peat - 6 yr old"
 
 #remove other dataframes
-rm(yearly); rm(daily); rm(peat6_eddy); rm(peat6_met)
+rm(yearly); rm(daily);

### 2017-07-12 R/Diel_patterns.R
fix load issues

@@ -4,7 +4,11 @@
 #'
 #' @import dplyr
 #' @importFrom dplyr "%>%"
-#' @importFrom lubridate month
+
+# load eddy flux and met dataset
+load("data/peat6_all.Rda")
+load("data/peat19_all.Rda")
+load("data/alluvium_all.Rda")
 
 ## Process each core site into diel values then we will merge them into a single file for visualization
 # diel fluxes from 6yr old peat site

### 2017-07-12 R/soils.R
Fixes to remove read_csv use

@@ -3,12 +3,11 @@
 #' Sites: Peat 20 yr old, Alluvium 4 yr old. More to follow
 #'
 #' @import dplyr
-#' @importFrom readr read_csv
 #' @importFrom dplyr "%>%"
 
 #load data.frames for pH and iron
-pH_data <- read_csv("data/pH.csv")
-Fe_data <- read_csv("data/Fe_data.csv")
+pH_data <- read.csv("data/pH.csv")
+Fe_data <- read.csv("data/Fe_data.csv")
 
 #clean data tables to remove empty columns and rows
 pH_data <- pH_data[,colSums(is.na(pH_data))<nrow(pH_data)] #columns
@@ -19,9 +18,9 @@ Fe_data <- na.omit(Fe_data) #rows
 
 #merge data sources to single dataframe, clean up remaining dataframe
 soils_df <- merge(pH_data, Fe_data, by="Number") %>%
-  select(Number, `Depth (cm).x`, Tract.x, Point.x, Area.x, pH, `Fe(II)_mg.g`,
-         Fe_all_mg.g, `Fe(III)_mg.g`) %>%
-  rename(Depth = `Depth (cm).x`, FeII_mg.g = `Fe(II)_mg.g`, FeIII_mg.g = `Fe(III)_mg.g`)
+  select(Number, Depth..cm..x, Tract.x, Point.x, Area.x, pH, Fe.II._mg.g,
+         Fe_all_mg.g, Fe.III._mg.g) %>%
+  rename(Depth = Depth..cm..x, FeII_mg.g = Fe.II._mg.g, FeIII_mg.g = Fe.III._mg.g)
 
 #create site variable based on 'Area' site names
 soils_df$site <- ifelse(soils_df$Area.x == "East End", "Alluvium - 3 yr old",

### 2017-07-12 R/soils.R
tests

@@ -1,5 +1,4 @@
 #' Script to process soils data across sites
-#'
 #' Sites: Peat 20 yr old, Alluvium 4 yr old. More to follow
 #'
 #' @import dplyr

### 2017-07-12 R/Diel_patterns.R
data cleanup

@@ -6,9 +6,9 @@
 #' @importFrom dplyr "%>%"
 
 # load eddy flux and met dataset
-load("data/peat6_all.Rda")
-load("data/peat19_all.Rda")
-load("data/alluvium_all.Rda")
+load("data/peat6_all.Rdata")
+load("data/peat19_all.Rdata")
+load("data/alluvium_all.Rdata")
 
 ## Process each core site into diel values then we will merge them into a single file for visualization
 # diel fluxes from 6yr old peat site

### 2017-07-12 R/alluvium_processing.R

@@ -7,7 +7,7 @@
 #' @importFrom zoo na.approx
 
 # load eddy flux and met dataset
-load("data/alluvium_all.Rda")
+load("data/alluvium_all.Rdata")
 
 # create a long-term water temperature measure, as the probes have changed over time
 # when we don't have a 10cm water temp measurement, add 8cm depth in place

### 2017-07-12 R/peat19_processing.R

@@ -6,7 +6,7 @@
 #' @importFrom dplyr "%>%"
 
 # load eddy flux and met dataset
-load("data/peat19_all.Rda")
+load("data/peat19_all.Rdata")
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat19_all %>%

### 2017-07-12 R/peat6_processing.R

@@ -6,7 +6,7 @@
 #' @importFrom dplyr "%>%"
 
 # load eddy flux and met dataset
-load("data/peat6_all.Rda")
+load("data/peat6_all.Rdata")
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat6_all %>%

### 2017-07-13 R/Diel_patterns.R
Figure changes

@@ -17,8 +17,8 @@ diel_peat6 <- peat6_all %>%
   group_by(year, time, site) %>%
   summarise(CH4 = mean(wm, na.rm=T),
             sdCH4 = sd(wm, na.rm=T),
-            GPP = mean(wc, na.rm=T),
-            sdGPP = sd(wc, na.rm=T),
+            NEE = mean(wc, na.rm=T),
+            sdNEE = sd(wc, na.rm=T),
             ET = mean(wq, na.rm=T),
             sdET = sd(wq, na.rm=T),
             Ta = mean(TA.y, na.rm=T),
@@ -34,8 +34,8 @@ diel_peat19 <- peat19_all %>%
   group_by(year, time, site) %>%
   summarise(CH4 = mean(wm, na.rm=T),
             sdCH4 = sd(wm, na.rm=T),
-            GPP = mean(wc, na.rm=T),
-            sdGPP = sd(wc, na.rm=T),
+            NEE = mean(wc, na.rm=T),
+            sdNEE = sd(wc, na.rm=T),
             ET = mean(wq, na.rm=T),
             sdET = sd(wq, na.rm=T),
             Ta = mean(TA.y, na.rm=T),
@@ -47,12 +47,12 @@ diel_peat19 <- peat19_all %>%
 
 #diel fluxes for 4yr old alluvium site
 diel_alluvium <- alluvium_all %>%
-  subset(DOY.x < 301 & DOY.x > 99) %>% #use growing season only
+  subset(DOY.x < 301 & DOY.x > 99 & year > 2013) %>% #use growing season only
   group_by(year, time, site) %>%
   summarise(CH4 = mean(wm, na.rm=T),
             sdCH4 = sd(wm, na.rm=T),
-            GPP = mean(wc, na.rm=T),
-            sdGPP = sd(wc, na.rm=T),
+            NEE = mean(wc, na.rm=T),
+            sdNEE = sd(wc, na.rm=T),
             ET = mean(wq, na.rm=T),
             sdET = sd(wq, na.rm=T),
             Ta = mean(TA.y, na.rm=T),

### 2017-08-03 R/soils.R
Many updates for full manuscript processing

@@ -4,35 +4,22 @@
 #' @import dplyr
 #' @importFrom dplyr "%>%"
 
-#load data.frames for pH and iron
-pH_data <- read.csv("data/pH.csv")
-Fe_data <- read.csv("data/Fe_data.csv")
-
-#clean data tables to remove empty columns and rows
-pH_data <- pH_data[,colSums(is.na(pH_data))<nrow(pH_data)] #columns
-pH_data <- na.omit(pH_data) #rows
-
-Fe_data <- Fe_data[,colSums(is.na(Fe_data))<nrow(Fe_data)] #columns
-Fe_data <- na.omit(Fe_data) #rows
-
-#merge data sources to single dataframe, clean up remaining dataframe
-soils_df <- merge(pH_data, Fe_data, by="Number") %>%
-  select(Number, Depth..cm..x, Tract.x, Point.x, Area.x, pH, Fe.II._mg.g,
-         Fe_all_mg.g, Fe.III._mg.g) %>%
-  rename(Depth = Depth..cm..x, FeII_mg.g = Fe.II._mg.g, FeIII_mg.g = Fe.III._mg.g)
+#load soils data
+soils_df <- read.csv("data/soils.csv")
 
 #create site variable based on 'Area' site names
-soils_df$site <- ifelse(soils_df$Area.x == "East End", "Alluvium - 3 yr old",
-                        "Peat - 19 yr old")
+soils_df$site <- ifelse(soils_df$Area == "East End", "Alluvium - 3 yr old",
+                        ifelse(soils_df$Area == "West Pond", "Peat - 19 yr old",
+                               "Peat - 6 yr old"))
 
 #What percent of iron is in oxidized form?
-soils_df$percent_ox <- (soils_df$FeIII_mg.g/soils_df$Fe_all_mg.g)*100
-soils_df$percent_ox <- ifelse(soils_df$FeIII_mg.g < 0, 0, soils_df$percent_ox) #if FeIII is less than zero set to zero
+soils_df$percent_ox <- (soils_df$FeIII_mg.g/soils_df$FeT_mg.g)*100
+soils_df$percent_ox <- ifelse(soils_df$FeT_mg.g <= 0, NA, soils_df$percent_ox) #if no measurable Fe set to zero
 
 #New surface v. deep column represents more accurately that we are comparing a recent muck layer
 # to a deep older soil layer. This deep layer at the peat site is actually ~0.7m below surface
[…]

### 2017-08-29 R/alluvium_processing.R
results working updates

@@ -67,9 +67,9 @@ yearly$GHGbalance <- (yearly$tNEE*44/12) + (25*yearly$tCH4*16/12) #CO2-eq m-2 yr
 #resave with specific names, and add site name variable
 alluvium_yearly <- yearly
 alluvium_daily <- daily
-alluvium_yearly$site <- "Alluvium - 3 yr old"
-alluvium_daily$site <- "Alluvium - 3 yr old"
-alluvium_all$site <- "Alluvium - 3 yr old"
+alluvium_yearly$site <- "Alluvium"
+alluvium_daily$site <- "Alluvium"
+alluvium_all$site <- "Alluvium"
 
 #remove other dataframes
 rm(yearly); rm(daily);

### 2017-08-29 R/peat19_processing.R

@@ -61,9 +61,9 @@ yearly$GHGbalance <- (yearly$tNEE*44/12) + (25*yearly$tCH4*16/12) #CO2-eq m-2 yr
 #resave with specific names, and add a site name variable
 peat19_yearly <- yearly
 peat19_daily <- daily
-peat19_yearly$site <- "Peat - 19 yr old"
-peat19_daily$site <- "Peat - 19 yr old"
-peat19_all$site <- "Peat - 19 yr old"
+peat19_yearly$site <- "Old Peat"
+peat19_daily$site <- "Old Peat"
+peat19_all$site <- "Old Peat"
 
 #remove other dataframes
 rm(yearly); rm(daily);

### 2017-08-29 R/peat6_processing.R

@@ -61,9 +61,9 @@ yearly$GHGbalance <- (yearly$tNEE*44/12) + (25*yearly$tCH4*16/12) #CO2-eq m-2 yr
 #resave with specific names, and add a site name variable
 peat6_yearly <- yearly
 peat6_daily <- daily
-peat6_yearly$site <- "Peat - 6 yr old"
-peat6_daily$site <- "Peat - 6 yr old"
-peat6_all$site <- "Peat - 6 yr old"
+peat6_yearly$site <- "Young Peat"
+peat6_daily$site <- "Young Peat"
+peat6_all$site <- "Young Peat"
 
 #remove other dataframes
 rm(yearly); rm(daily);

### 2017-08-29 R/soils.R

@@ -8,9 +8,9 @@
 soils_df <- read.csv("data/soils.csv")
 
 #create site variable based on 'Area' site names
-soils_df$site <- ifelse(soils_df$Area == "East End", "Alluvium - 3 yr old",
-                        ifelse(soils_df$Area == "West Pond", "Peat - 19 yr old",
-                               "Peat - 6 yr old"))
+soils_df$site <- ifelse(soils_df$Area == "East End", "Alluvium",
+                        ifelse(soils_df$Area == "West Pond", "Old Peat",
+                               "Young Peat"))
 
 #What percent of iron is in oxidized form?
 soils_df$percent_ox <- (soils_df$FeIII_mg.g/soils_df$FeT_mg.g)*100
@@ -18,8 +18,8 @@ soils_df$percent_ox <- ifelse(soils_df$FeT_mg.g <= 0, NA, soils_df$percent_ox) #
 
 #New surface v. deep column represents more accurately that we are comparing a recent muck layer
 # to a deep older soil layer. This deep layer at the peat site is actually ~0.7m below surface
-soils_df$horizon <- ifelse(soils_df$Depth == "0-15", "surface", "deep")
+soils_df$horizon <- ifelse(soils_df$Depth == "0-15", "Recent", "Parent")
 
 #Also, need to fix West Pond point 1 where 15-30 was also 'surface' litter
 soils_df$horizon <- ifelse(soils_df$Area == "West Pond" & soils_df$Point == "P1",
-                           "surface", soils_df$horizon)
+                           "Recent", soils_df$horizon)

### 2017-08-30 R/soils.R
Rename soil classification and more writing in the results section

@@ -18,8 +18,8 @@ soils_df$percent_ox <- ifelse(soils_df$FeT_mg.g <= 0, NA, soils_df$percent_ox) #
 
 #New surface v. deep column represents more accurately that we are comparing a recent muck layer
 # to a deep older soil layer. This deep layer at the peat site is actually ~0.7m below surface
-soils_df$horizon <- ifelse(soils_df$Depth == "0-15", "Recent", "Parent")
+soils_df$horizon <- ifelse(soils_df$Depth == "0-15", "Accreted", "Parent")
 
 #Also, need to fix West Pond point 1 where 15-30 was also 'surface' litter
 soils_df$horizon <- ifelse(soils_df$Area == "West Pond" & soils_df$Point == "P1",
-                           "Recent", soils_df$horizon)
+                           "Accreted", soils_df$horizon)

### 2017-08-31 R/alluvium_processing.R
Results writing and figure improvement

@@ -39,7 +39,7 @@ daily <- alluvium_all %>%
             Cond = mean(Cond, na.rm=T),        #conductivity (mS)
             month = round(median(month)),
             year = round(median(year))) %>%
-  filter(year < 2017) #only pre-2017 data
+  filter(year > 2013) #cut out pre-wetland measures
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2013-01-01")

### 2017-08-31 R/peat6_processing.R

@@ -33,7 +33,7 @@ daily <- peat6_all %>%
             Cond = mean(Cond, na.rm=T),        #conductivity (mS)
             month = round(median(month)),
             year = round(median(year))) %>%
-  filter(year < 2017) #only pre-2017
+  filter(year > 2010) #cut pre-wetland measures
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2010-01-01")

### 2017-09-05 R/alluvium_processing.R
Lots of new analysis and results work

@@ -16,7 +16,7 @@ alluvium_all$TW_10cm <- na.approx(alluvium_all$TW_10cm, na.rm=F) # linear interp
 
 #Simple average of daily fluxes for pre-gapfilled values
 daily <- alluvium_all %>%
-  group_by(dday) %>%
+  group_by(dday, site) %>%
   summarise(mNEE = mean(wc_gf),         #NEE (umol m-2 s-1)
             c_obs = sum(!is.na(wc)),    #num of non-filled observations (applies all _obs)
             mCH4 = mean(wm_gf),         #CH4 flux (nmol m-2 s-1)
@@ -39,7 +39,7 @@ daily <- alluvium_all %>%
             Cond = mean(Cond, na.rm=T),        #conductivity (mS)
             month = round(median(month)),
             year = round(median(year))) %>%
-  filter(year > 2013) #cut out pre-wetland measures
+  filter(year > 2013 & year < 2017) #cut out pre-wetland measures/incomplete years
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2013-01-01")
@@ -50,7 +50,7 @@ daily$gGEP <- (daily$GPP*12.01*3600*24)/1000000   #g C m-2 d-1
 
 #Annual fluxes from daily fluxes
 yearly <- daily %>%
-  group_by(year) %>%
+  group_by(year, site) %>%
   summarise(tCH4 = mean(mgCH4)*365/1000, #gC m-2 yr-1 (same for all fluxes below)
             tNEE = mean(gCO2)*365,
             tER = mean(gER)*365,
@@ -67,9 +67,6 @@ yearly$GHGbalance <- (yearly$tNEE*44/12) + (25*yearly$tCH4*16/12) #CO2-eq m-2 yr
 #resave with specific names, and add site name variable
 alluvium_yearly <- yearly
 alluvium_daily <- daily
-alluvium_yearly$site <- "Alluvium"
-alluvium_daily$site <- "Alluvium"
-alluvium_all$site <- "Alluvium"
 
 #remove other dataframes
 rm(yearly); rm(daily);

### 2017-09-05 R/peat19_processing.R

@@ -10,7 +10,7 @@ load("data/peat19_all.Rdata")
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat19_all %>%
-  group_by(dday) %>%
+  group_by(dday, site) %>%
   summarise(mNEE = mean(wc_gf),         #NEE (umol m-2 s-1)
             c_obs = sum(!is.na(wc)),    #num of non-filled observations (applies all _obs)
             mCH4 = mean(wm_gf),         #CH4 flux (nmol m-2 s-1)
@@ -33,7 +33,7 @@ daily <- peat19_all %>%
             Cond = mean(conductivity, na.rm=T), #conductivity (mS)
             month = round(median(month)),
             year = round(median(year))) %>%
-  filter(year < 2017) #only pre-2017
+  filter(year < 2017)
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2012-01-01")
@@ -44,7 +44,7 @@ daily$gGEP <- (daily$GPP*12.01*3600*24)/1000000   #g C m-2 d-1
 
 #Annual fluxes from daily fluxes
 yearly <- daily %>%
-  group_by(year) %>%
+  group_by(year, site) %>%
   summarise(tCH4 = mean(mgCH4)*365/1000, #gC m-2 yr-1 (same for all fluxes below)
             tNEE = mean(gCO2)*365,
             tER = mean(gER)*365,
@@ -61,9 +61,6 @@ yearly$GHGbalance <- (yearly$tNEE*44/12) + (25*yearly$tCH4*16/12) #CO2-eq m-2 yr
 #resave with specific names, and add a site name variable
 peat19_yearly <- yearly
 peat19_daily <- daily
-peat19_yearly$site <- "Old Peat"
-peat19_daily$site <- "Old Peat"
-peat19_all$site <- "Old Peat"
 
 #remove other dataframes
 rm(yearly); rm(daily);

### 2017-09-05 R/peat6_processing.R

@@ -10,7 +10,7 @@ load("data/peat6_all.Rdata")
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat6_all %>%
-  group_by(dday) %>%
+  group_by(dday, site) %>%
   summarise(mNEE = mean(wc_gf),         #NEE (umol m-2 s-1)
             c_obs = sum(!is.na(wc)),    #num of non-filled observations (applies all _obs)
             mCH4 = mean(wm_gf),         #CH4 flux (nmol m-2 s-1)
@@ -44,7 +44,7 @@ daily$gGEP <- (daily$GPP*12.01*3600*24)/1000000   #g C m-2 d-1
 
 #Annual fluxes from daily fluxes
 yearly <- daily %>%
-  group_by(year) %>%
+  group_by(year, site) %>%
   summarise(tCH4 = mean(mgCH4)*365/1000, #gC m-2 yr-1 (same for all fluxes below)
             tNEE = mean(gCO2)*365,
             tER = mean(gER)*365,
@@ -61,9 +61,6 @@ yearly$GHGbalance <- (yearly$tNEE*44/12) + (25*yearly$tCH4*16/12) #CO2-eq m-2 yr
 #resave with specific names, and add a site name variable
 peat6_yearly <- yearly
 peat6_daily <- daily
-peat6_yearly$site <- "Young Peat"
-peat6_daily$site <- "Young Peat"
-peat6_all$site <- "Young Peat"
 
 #remove other dataframes
 rm(yearly); rm(daily);

### 2017-09-06 R/alluvium_processing.R
new figures and results work

@@ -39,7 +39,7 @@ daily <- alluvium_all %>%
             Cond = mean(Cond, na.rm=T),        #conductivity (mS)
             month = round(median(month)),
             year = round(median(year))) %>%
-  filter(year > 2013 & year < 2017) #cut out pre-wetland measures/incomplete years
+  filter(year > 2013) #cut out pre-wetland measures/incomplete years
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2013-01-01")

### 2017-09-06 R/peat19_processing.R

@@ -32,8 +32,7 @@ daily <- peat19_all %>%
             WTD = mean(WT, na.rm=T),    #water table (m from surface)
             Cond = mean(conductivity, na.rm=T), #conductivity (mS)
             month = round(median(month)),
-            year = round(median(year))) %>%
-  filter(year < 2017)
+            year = round(median(year)))
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2012-01-01")

### 2017-09-06 R/Diel_patterns.R
writing and updates

@@ -26,7 +26,9 @@ diel_peat6 <- peat6_all %>%
             Tw = mean(TW_TULE_10cm, na.rm=T),
             sdTw = sd(TW_TULE_10cm, na.rm=T),
             PAR = mean(PAR, na.rm=T),
-            sdPAR = sd(PAR, na.rm=T))
+            sdPAR = sd(PAR, na.rm=T),
+            PA = mean(PA.y, na.rm=T),
+            sdPA = sd(PA.y, na.rm=T))
 
 #diel fluxes for 19yr old peat site
 diel_peat19 <- peat19_all %>%
@@ -43,7 +45,9 @@ diel_peat19 <- peat19_all %>%
             Tw = mean(TW_8cm, na.rm=T),
             sdTw = sd(TW_8cm, na.rm=T),
             PAR = mean(PAR, na.rm=T),
-            sdPAR = sd(PAR, na.rm=T))
+            sdPAR = sd(PAR, na.rm=T),
+            PA = mean(PA.y, na.rm=T),
+            sdPA = sd(PA.y, na.rm=T))
 
 #diel fluxes for 4yr old alluvium site
 diel_alluvium <- alluvium_all %>%
@@ -60,7 +64,9 @@ diel_alluvium <- alluvium_all %>%
             Tw = mean(TW_10cm, na.rm=T),
             sdTw = sd(TW_10cm, na.rm=T),
             PAR = mean(PAR, na.rm=T),
-            sdPAR = sd(PAR, na.rm=T))
+            sdPAR = sd(PAR, na.rm=T),
+            PA = mean(PA.y, na.rm=T),
+            sdPA = sd(PA.y, na.rm=T))
 
 #merge core site files
 diel_all <- rbind(diel_peat6, diel_peat19); diel_all <- rbind(diel_all, diel_alluvium);

### 2017-09-06 R/alluvium_processing.R

@@ -37,9 +37,10 @@ daily <- alluvium_all %>%
             Rain = sum(PRECIP, na.rm=T),       #rain (mm)
             WTD = mean(WT, na.rm=T),           #water table (m from surface)
             Cond = mean(Cond, na.rm=T),        #conductivity (mS)
+            t_obs = length(wc_gf),      # total observations in the day
             month = round(median(month)),
             year = round(median(year))) %>%
-  filter(year > 2013) #cut out pre-wetland measures/incomplete years
+  filter(year > 2013 & t_obs == 48) #cut out pre-wetland measures, and incomplete days at edge of time series
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2013-01-01")

### 2017-09-06 R/peat19_processing.R

@@ -31,8 +31,10 @@ daily <- peat19_all %>%
             Rain = 1,
             WTD = mean(WT, na.rm=T),    #water table (m from surface)
             Cond = mean(conductivity, na.rm=T), #conductivity (mS)
+            t_obs = length(wc_gf),      # total observations in the day
             month = round(median(month)),
-            year = round(median(year)))
+            year = round(median(year))) %>%
+  filter(t_obs == 48)  #remove incomplete days at either end of time series
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2012-01-01")

### 2017-09-06 R/peat6_processing.R

@@ -31,9 +31,10 @@ daily <- peat6_all %>%
             Rain = sum(PRECIP, na.rm=T),       #rain (mm)
             WTD = mean(WT, na.rm=T),           #water table (m from surface)
             Cond = mean(Cond, na.rm=T),        #conductivity (mS)
+            t_obs = length(wc_gf),      # total observations in the day
             month = round(median(month)),
             year = round(median(year))) %>%
-  filter(year > 2010) #cut pre-wetland measures
+  filter(year > 2010 & t_obs == 48) #cut pre-wetland measures, and incomplete days at ends of time series
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2010-01-01")

### 2017-09-08 R/soils.R
Soils additions

@@ -14,7 +14,7 @@ soils_df$site <- ifelse(soils_df$Area == "East End", "Alluvium",
 
 #What percent of iron is in oxidized form?
 soils_df$percent_ox <- (soils_df$FeIII_mg.g/soils_df$FeT_mg.g)*100
-soils_df$percent_ox <- ifelse(soils_df$FeT_mg.g <= 0, NA, soils_df$percent_ox) #if no measurable Fe set to zero
+soils_df$percent_ox <- ifelse(soils_df$FeT_mg.g <= 1, NA, soils_df$percent_ox) #if no measurable Fe set to zero
 
 #New surface v. deep column represents more accurately that we are comparing a recent muck layer
 # to a deep older soil layer. This deep layer at the peat site is actually ~0.7m below surface

### 2017-09-18 R/DO_processing.R
Completed draft w/ additional DO processing scratch analysis

@@ -1,0 +1,8 @@
+test <- select(DO_data, -Mdate_met, -X9)
+
+test <- gather(test, site, DO, -decday)
+test <- subset(test, site != "TT_DO")
+
+
+ggplot(test, aes(x=site, y=DO)) +
+  geom_boxplot()

### 2017-09-20 README.Rmd
ReadMe update

@@
 
-The goal of WetlandComparison is to make a first attempt at a reproducible research R package. This will still be somewhat hampered by the fact that much of this research is conducted with Matlab.
+This package was used the generate the manuscript "Effect of soil iron content and sediment accretion on methane fluxes from restored wetlands." by Samuel D.
+Chamberlain et.
+al.
+This was my first attempt at a reproducible research example, and it follows the R package structure adapted from Carl Boettiger's template found here: https://github.com/cboettig/template.
+Briefly, the /data folder contains soil and half-hourly eddy covariance files used in the analysis, the /R folder contains scripts used to process data, and the /vignettes folder contains the Markdown and bibiography files used to generate the manuscript, as well as two figure images that were not directly reproducible in R.
+Additionally, /man and /test folders are standard in R packages but are not particularly relevant to this manuscript as functions are not introduced in this package.
+They are included anyway to follow convention.
+
+Figure 1 and 7 are not directly reproducible in R, but all other analyses herein are reproducible in this package.
+Figure 1 was generated in ArcMap using the soil series data downloaded from the USDA Web Soil Survey (https://websoilsurvey.sc.egov.usda.gov/), and flux footprints generated from our half-hourly flux data using 2D analytical footprint models described in Detto et al.
+2006.
+Figure 7 was generated using a combined information theory-wavelet time series decomposition using a modification of the MATLAB ProcessNetwork Software found here: https://github.com/samdchamberlain/ProcessNetwork_Software.
+All other analyses in this work are reproducible from the 'manuscript.Rmd' file in the /vignettes folder, and running this file will reproduce this manuscript in its entirety.
 
@@
 
-## Example
-
-This is a basic example which shows you how to solve a common problem:
-
-```{r example}
-## basic example code
-```
+## How to Run
+Load package into RStudio and open the 'manuscript.Rmd' within the /vignettes folder.
+Using RStudio, click the 'Knit' button at the top of the console and this manuscript, and analyses herein, will be re-created.

### 2017-09-20 R/DO_processing.R

@@ -1,8 +1,0 @@
-test <- select(DO_data, -Mdate_met, -X9)
-
-test <- gather(test, site, DO, -decday)
-test <- subset(test, site != "TT_DO")
-
-
-ggplot(test, aes(x=site, y=DO)) +
-  geom_boxplot()

### 2017-09-25 R/alluvium_processing.R
revisions

@@ -18,11 +18,14 @@ alluvium_all$TW_10cm <- na.approx(alluvium_all$TW_10cm, na.rm=F) # linear interp
 daily <- alluvium_all %>%
   group_by(dday, site) %>%
   summarise(mNEE = mean(wc_gf),         #NEE (umol m-2 s-1)
+            vNEE = mean(wc_gf_var),     #NEE variance (umol m-2 s-1)^2
             c_obs = sum(!is.na(wc)),    #num of non-filled observations (applies all _obs)
             mCH4 = mean(wm_gf),         #CH4 flux (nmol m-2 s-1)
+            vCH4 = mean(wm_gf_var),     #CH4 variance (nmol m-2 s-1)^2
             m_obs = sum(!is.na(wm)),
             GPP = mean(gpp_ANNnight),   #partitioned GPP (umol m-2 s-1)
             ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
+            vER = mean(er_ANN_var),     #partitioned respiration variance (umol m-2 s-1)^2
             ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
             q_obs = sum(!is.na(wq)),
             H = mean(H_gf),                    #sensible heat flux (W m-2)
@@ -53,8 +56,11 @@ daily$gGEP <- (daily$GPP*12.01*3600*24)/1000000   #g C m-2 d-1
 yearly <- daily %>%
   group_by(year, site) %>%
   summarise(tCH4 = mean(mgCH4)*365/1000, #gC m-2 yr-1 (same for all fluxes below)
+            ciCH4 = 1.96*(sqrt(mean(vCH4)*(12.01*3600*24*365/(10^9))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tNEE = mean(gCO2)*365,
+            ciNEE = 1.96*(sqrt(mean(vNEE)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tER = mean(gER)*365,
+            ciER = 1.96*(sqrt(mean(vER)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tGEP = mean(gGEP)*365,
             Tair = mean(Tair, na.rm=T),
             GCC = mean(mGCC, na.rm=T),

### 2017-09-25 R/peat19_processing.R

@@ -12,11 +12,14 @@ load("data/peat19_all.Rdata")
 daily <- peat19_all %>%
   group_by(dday, site) %>%
   summarise(mNEE = mean(wc_gf),         #NEE (umol m-2 s-1)
+            vNEE = mean(wc_gf_var),     #NEE variance (umol m-2 s-1)^2
             c_obs = sum(!is.na(wc)),    #num of non-filled observations (applies all _obs)
             mCH4 = mean(wm_gf),         #CH4 flux (nmol m-2 s-1)
+            vCH4 = mean(wm_gf_var),     #CH4 variance (nmol m-2 s-1)^2
             m_obs = sum(!is.na(wm)),
             GPP = mean(gpp_ANNnight),   #partitioned GPP (umol m-2 s-1)
             ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
+            vER = mean(er_ANN_var),     #partitioned respiration variance (umol m-2 s-1)^2
             ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
             q_obs = sum(!is.na(wq)),
             H = mean(H_gf),             #sensible heat flux (W m-2)
@@ -47,8 +50,11 @@ daily$gGEP <- (daily$GPP*12.01*3600*24)/1000000   #g C m-2 d-1
 yearly <- daily %>%
   group_by(year, site) %>%
   summarise(tCH4 = mean(mgCH4)*365/1000, #gC m-2 yr-1 (same for all fluxes below)
+            ciCH4 = 1.96*(sqrt(mean(vCH4)*(12.01*3600*24*365/(10^9))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tNEE = mean(gCO2)*365,
+            ciNEE = 1.96*(sqrt(mean(vNEE)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tER = mean(gER)*365,
+            ciER = 1.96*(sqrt(mean(vER)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tGEP = mean(gGEP)*365,
             Tair = mean(Tair, na.rm=T),
             GCC = mean(mGCC, na.rm=T),

### 2017-09-25 R/peat6_processing.R

@@ -12,11 +12,14 @@ load("data/peat6_all.Rdata")
 daily <- peat6_all %>%
   group_by(dday, site) %>%
   summarise(mNEE = mean(wc_gf),         #NEE (umol m-2 s-1)
+            vNEE = mean(wc_gf_var),     #NEE variance (umol m-2 s-1)^2
             c_obs = sum(!is.na(wc)),    #num of non-filled observations (applies all _obs)
             mCH4 = mean(wm_gf),         #CH4 flux (nmol m-2 s-1)
+            vCH4 = mean(wm_gf_var),     #CH4 variance (nmol m-2 s-1)^2
             m_obs = sum(!is.na(wm)),
             GPP = mean(gpp_ANNnight),   #partitioned GPP (umol m-2 s-1)
             ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
+            vER = mean(er_ANN_var),     #partitioned respiration variance (umol m-2 s-1)^2
             ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
             q_obs = sum(!is.na(wq)),
             H = mean(H_gf),                    #sensible heat flux (W m-2)
@@ -47,8 +50,11 @@ daily$gGEP <- (daily$GPP*12.01*3600*24)/1000000   #g C m-2 d-1
 yearly <- daily %>%
   group_by(year, site) %>%
   summarise(tCH4 = mean(mgCH4)*365/1000, #gC m-2 yr-1 (same for all fluxes below)
+            ciCH4 = 1.96*(sqrt(mean(vCH4)*(12.01*3600*24*365/(10^9))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tNEE = mean(gCO2)*365,
+            ciNEE = 1.96*(sqrt(mean(vNEE)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tER = mean(gER)*365,
+            ciER = 1.96*(sqrt(mean(vER)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tGEP = mean(gGEP)*365,
             Tair = mean(Tair, na.rm=T),
             GCC = mean(mGCC, na.rm=T),

### 2017-09-27 R/soils.R
first pass revisions

@@ -8,7 +8,7 @@
 soils_df <- read.csv("data/soils.csv")
 
 #create site variable based on 'Area' site names
-soils_df$site <- ifelse(soils_df$Area == "East End", "Alluvium",
+soils_df$site <- ifelse(soils_df$Area == "East End", "Peat-Alluvium",
                         ifelse(soils_df$Area == "West Pond", "Old Peat",
                                "Young Peat"))
 
@@ -23,3 +23,6 @@ soils_df$horizon <- ifelse(soils_df$Depth == "0-15", "Accreted", "Parent")
 #Also, need to fix West Pond point 1 where 15-30 was also 'surface' litter
 soils_df$horizon <- ifelse(soils_df$Area == "West Pond" & soils_df$Point == "P1",
                            "Accreted", soils_df$horizon)
+
+#re-order factors to group peat sites in legend
+soils_df$site <- factor(soils_df$site, levels=c("Peat-Alluvium", "Old Peat", "Young Peat"))

### 2017-09-27 R/alluvium_processing.R
completed Dennis revisions

@@ -69,7 +69,8 @@ yearly <- daily %>%
 
 #Ecosystem C balance and GHG (CO2eq) balance
 yearly$Cbalance <- yearly$tNEE + yearly$tCH4 #C m-2 yr-1
-yearly$GHGbalance <- (yearly$tNEE*44/12) + (25*yearly$tCH4*16/12) #CO2-eq m-2 yr-1
+yearly$GHGbalance <- (yearly$tNEE*44/12) + (45*yearly$tCH4*16/12) #CO2-eq m-2 yr-1 using 45x SGWP (Neubauer and Megonigal 2015)
+yearly$ciGHG <- (yearly$ciNEE*44/12) + (45*yearly$ciCH4*16/12)
 
 #resave with specific names, and add site name variable
 alluvium_yearly <- yearly

### 2017-09-27 R/peat19_processing.R

@@ -63,7 +63,8 @@ yearly <- daily %>%
 
 #Ecosystem C balance and GHG (CO2eq) balance
 yearly$Cbalance <- yearly$tNEE + yearly$tCH4 #C m-2 yr-1
-yearly$GHGbalance <- (yearly$tNEE*44/12) + (25*yearly$tCH4*16/12) #CO2-eq m-2 yr-1
+yearly$GHGbalance <- (yearly$tNEE*44/12) + (45*yearly$tCH4*16/12)  #CO2-eq m-2 yr-1 using 45x SGWP (Neubauer and Megonigal 2015)
+yearly$ciGHG <- (yearly$ciNEE*44/12) + (45*yearly$ciCH4*16/12)
 
 #resave with specific names, and add a site name variable
 peat19_yearly <- yearly

### 2017-09-27 R/peat6_processing.R

@@ -63,7 +63,8 @@ yearly <- daily %>%
 
 #Ecosystem C balance and GHG (CO2eq) balance
 yearly$Cbalance <- yearly$tNEE + yearly$tCH4 #C m-2 yr-1
-yearly$GHGbalance <- (yearly$tNEE*44/12) + (25*yearly$tCH4*16/12) #CO2-eq m-2 yr-1
+yearly$GHGbalance <- (yearly$tNEE*44/12) + (45*yearly$tCH4*16/12)  #CO2-eq m-2 yr-1 using 45x SGWP (Neubauer and Megonigal 2015)
+yearly$ciGHG <- (yearly$ciNEE*44/12) + (45*yearly$ciCH4*16/12)
 
 #resave with specific names, and add a site name variable
 peat6_yearly <- yearly

### 2017-09-28 R/alluvium_processing.R
shortened abstract and other edits

@@ -24,6 +24,7 @@ daily <- alluvium_all %>%
             vCH4 = mean(wm_gf_var),     #CH4 variance (nmol m-2 s-1)^2
             m_obs = sum(!is.na(wm)),
             GPP = mean(gpp_ANNnight),   #partitioned GPP (umol m-2 s-1)
+            vGPP = mean(wc_gf_var)+mean(er_ANN_var), #error propogation for calculated GPP (NEE-ER)
             ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
             vER = mean(er_ANN_var),     #partitioned respiration variance (umol m-2 s-1)^2
             ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
@@ -62,6 +63,7 @@ yearly <- daily %>%
             tER = mean(gER)*365,
             ciER = 1.96*(sqrt(mean(vER)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tGEP = mean(gGEP)*365,
+            ciGEP = 1.96*(sqrt(mean(vGPP)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANN (NEE-ER) differences
             Tair = mean(Tair, na.rm=T),
             GCC = mean(mGCC, na.rm=T),
             Days = sum(!is.na(mgCH4))) %>%
@@ -70,7 +72,7 @@ yearly <- daily %>%
 #Ecosystem C balance and GHG (CO2eq) balance
 yearly$Cbalance <- yearly$tNEE + yearly$tCH4 #C m-2 yr-1
 yearly$GHGbalance <- (yearly$tNEE*44/12) + (45*yearly$tCH4*16/12) #CO2-eq m-2 yr-1 using 45x SGWP (Neubauer and Megonigal 2015)
-yearly$ciGHG <- (yearly$ciNEE*44/12) + (45*yearly$ciCH4*16/12)
+yearly$ciGHG <- (yearly$ciNEE*44/12) + (45*yearly$ciCH4*16/12) #GHG balance 95% confidence interval
 
 #resave with specific names, and add site name variable
 alluvium_yearly <- yearly

### 2017-09-28 R/peat19_processing.R

@@ -18,6 +18,7 @@ daily <- peat19_all %>%
             vCH4 = mean(wm_gf_var),     #CH4 variance (nmol m-2 s-1)^2
             m_obs = sum(!is.na(wm)),
             GPP = mean(gpp_ANNnight),   #partitioned GPP (umol m-2 s-1)
+            vGPP = mean(wc_gf_var)+mean(er_ANN_var), #error propogation for calculated GPP (NEE-ER)
             ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
             vER = mean(er_ANN_var),     #partitioned respiration variance (umol m-2 s-1)^2
             ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
@@ -56,6 +57,7 @@ yearly <- daily %>%
             tER = mean(gER)*365,
             ciER = 1.96*(sqrt(mean(vER)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tGEP = mean(gGEP)*365,
+            ciGEP = 1.96*(sqrt(mean(vGPP)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANN (NEE-ER) differences
             Tair = mean(Tair, na.rm=T),
             GCC = mean(mGCC, na.rm=T),
             Days = sum(!is.na(mgCH4))) %>%
@@ -64,7 +66,7 @@ yearly <- daily %>%
 #Ecosystem C balance and GHG (CO2eq) balance
 yearly$Cbalance <- yearly$tNEE + yearly$tCH4 #C m-2 yr-1
 yearly$GHGbalance <- (yearly$tNEE*44/12) + (45*yearly$tCH4*16/12)  #CO2-eq m-2 yr-1 using 45x SGWP (Neubauer and Megonigal 2015)
-yearly$ciGHG <- (yearly$ciNEE*44/12) + (45*yearly$ciCH4*16/12)
+yearly$ciGHG <- (yearly$ciNEE*44/12) + (45*yearly$ciCH4*16/12) #GHG balance 95% confidence interval
 
 #resave with specific names, and add a site name variable
 peat19_yearly <- yearly

### 2017-09-28 R/peat6_processing.R

@@ -18,6 +18,7 @@ daily <- peat6_all %>%
             vCH4 = mean(wm_gf_var),     #CH4 variance (nmol m-2 s-1)^2
             m_obs = sum(!is.na(wm)),
             GPP = mean(gpp_ANNnight),   #partitioned GPP (umol m-2 s-1)
+            vGPP = mean(wc_gf_var)+mean(er_ANN_var), #error propogation for calculated GPP (NEE-ER)
             ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
             vER = mean(er_ANN_var),     #partitioned respiration variance (umol m-2 s-1)^2
             ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
@@ -56,6 +57,7 @@ yearly <- daily %>%
             tER = mean(gER)*365,
             ciER = 1.96*(sqrt(mean(vER)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANNs cumulative
             tGEP = mean(gGEP)*365,
+            ciGEP = 1.96*(sqrt(mean(vGPP)*(12.01*3600*24*365/(10^6))^2)/sqrt(20)), #95% confidence interval from 20 ANN (NEE-ER) differences
             Tair = mean(Tair, na.rm=T),
             GCC = mean(mGCC, na.rm=T),
             Days = sum(!is.na(mgCH4))) %>%
@@ -64,7 +66,7 @@ yearly <- daily %>%
 #Ecosystem C balance and GHG (CO2eq) balance
 yearly$Cbalance <- yearly$tNEE + yearly$tCH4 #C m-2 yr-1
 yearly$GHGbalance <- (yearly$tNEE*44/12) + (45*yearly$tCH4*16/12)  #CO2-eq m-2 yr-1 using 45x SGWP (Neubauer and Megonigal 2015)
-yearly$ciGHG <- (yearly$ciNEE*44/12) + (45*yearly$ciCH4*16/12)
+yearly$ciGHG <- (yearly$ciNEE*44/12) + (45*yearly$ciCH4*16/12) #GHG balance 95% confidence interval
 
 #resave with specific names, and add a site name variable
 peat6_yearly <- yearly

### 2017-10-28 R/soils.R
Cleaning package for publication

@@ -5,24 +5,24 @@
 #' @importFrom dplyr "%>%"
 
 #load soils data
-soils_df <- read.csv("data/soils.csv")
+load("data/soils.Rdata")
 
 #create site variable based on 'Area' site names
-soils_df$site <- ifelse(soils_df$Area == "East End", "Peat-Alluvium",
-                        ifelse(soils_df$Area == "West Pond", "Old Peat",
+soils$site <- ifelse(soils$Area == "East End", "Peat-Alluvium",
+                        ifelse(soils$Area == "West Pond", "Old Peat",
                                "Young Peat"))
 
 #What percent of iron is in oxidized form?
-soils_df$percent_ox <- (soils_df$FeIII_mg.g/soils_df$FeT_mg.g)*100
-soils_df$percent_ox <- ifelse(soils_df$FeT_mg.g <= 1, NA, soils_df$percent_ox) #if no measurable Fe set to zero
+soils$percent_ox <- (soils$FeIII_mg.g/soils$FeT_mg.g)*100
+soils$percent_ox <- ifelse(soils$FeT_mg.g <= 1, NA, soils$percent_ox) #if no measurable Fe set to zero
 
 #New surface v. deep column represents more accurately that we are comparing a recent muck layer
 # to a deep older soil layer. This deep layer at the peat site is actually ~0.7m below surface
-soils_df$horizon <- ifelse(soils_df$Depth == "0-15", "Accreted", "Parent")
+soils$horizon <- ifelse(soils$Depth == "0-15", "Accreted", "Parent")
 
 #Also, need to fix West Pond point 1 where 15-30 was also 'surface' litter
-soils_df$horizon <- ifelse(soils_df$Area == "West Pond" & soils_df$Point == "P1",
-                           "Accreted", soils_df$horizon)
+soils$horizon <- ifelse(soils$Area == "West Pond" & soils$Point == "P1",
+                           "Accreted", soils$horizon)
 
 #re-order factors to group peat sites in legend
-soils_df$site <- factor(soils_df$site, levels=c("Peat-Alluvium", "Old Peat", "Young Peat"))
+soils$site <- factor(soils$site, levels=c("Peat-Alluvium", "Old Peat", "Young Peat"))

### 2017-11-13 README.Rmd
travis updates

@@
 
-[![Travis-CI Build Status](https://travis-ci.org/samdchamberlain/WetlandComparison.svg?branch=master)](https://travis-ci.org/samdchamberlain/WetlandComparison)
+[![Travis-CI Build Status](https://travis-ci.org/samdchamberlain/wetlandcomparison.svg?branch=master)](https://travis-ci.org/samdchamberlain/wetlandcomparison)
 
@@
 ```{r gh-installation, eval = FALSE}
-# install.packages("devtools")
+install.packages("devtools")
 devtools::install_github("samdchamberlain/WetlandComparison")

### 2018-01-17 R/alluvium_processing.R
Beginning revisions

@@ -8,6 +8,7 @@
 
 # load eddy flux and met dataset
 load("data/alluvium_all.Rdata")
+alluvium_all$site <- "Alluvium"
 
 # create a long-term water temperature measure, as the probes have changed over time
 # when we don't have a 10cm water temp measurement, add 8cm depth in place
@@ -27,7 +28,7 @@ daily <- alluvium_all %>%
             vGPP = mean(wc_gf_var)+mean(er_ANN_var), #error propogation for calculated GPP (NEE-ER)
             ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
             vER = mean(er_ANN_var),     #partitioned respiration variance (umol m-2 s-1)^2
-            ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
+            ET = mean(wq_gf),           #evapotranspiration (mmol m-2 s-1)
             q_obs = sum(!is.na(wq)),
             H = mean(H_gf),                    #sensible heat flux (W m-2)
             mGCC = mean(GCC, na.rm=T),         #green index
@@ -52,6 +53,7 @@ daily$mgCH4 <- (daily$mCH4*12.01*3600*24)/1000000 #mg C m-2 d-1
 daily$gCO2 <- (daily$mNEE*12.01*3600*24)/1000000  #g C m-2 d-1
 daily$gER <- (daily$ER*12.01*3600*24)/1000000     #g C m-2 d-1
 daily$gGEP <- (daily$GPP*12.01*3600*24)/1000000   #g C m-2 d-1
+daily$mET <- (daily$ET*18.01528*3600*24)/1000000  #mm H2O d-1
 
 #Annual fluxes from daily fluxes
 yearly <- daily %>%

### 2018-01-17 R/peat19_processing.R

@@ -21,7 +21,7 @@ daily <- peat19_all %>%
             vGPP = mean(wc_gf_var)+mean(er_ANN_var), #error propogation for calculated GPP (NEE-ER)
             ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
             vER = mean(er_ANN_var),     #partitioned respiration variance (umol m-2 s-1)^2
-            ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
+            ET = mean(wq_gf),           #evapotranspiration (mmol m-2 s-1)
             q_obs = sum(!is.na(wq)),
             H = mean(H_gf),             #sensible heat flux (W m-2)
             mGCC = mean(GCC, na.rm=T),  #green index
@@ -38,7 +38,7 @@ daily <- peat19_all %>%
             t_obs = length(wc_gf),      # total observations in the day
             month = round(median(month)),
             year = round(median(year))) %>%
-  filter(t_obs == 48)  #remove incomplete days at either end of time series
+  filter(t_obs == 48 & year > 2013)  #remove incomplete days at either end of time series
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2012-01-01")
@@ -46,6 +46,7 @@ daily$mgCH4 <- (daily$mCH4*12.01*3600*24)/1000000 #mg C m-2 d-1
 daily$gCO2 <- (daily$mNEE*12.01*3600*24)/1000000  #g C m-2 d-1
 daily$gER <- (daily$ER*12.01*3600*24)/1000000     #g C m-2 d-1
 daily$gGEP <- (daily$GPP*12.01*3600*24)/1000000   #g C m-2 d-1
+daily$mET <- (daily$ET*18.01528*3600*24)/1000000  #mm H2O d-1
 
 #Annual fluxes from daily fluxes
 yearly <- daily %>%

### 2018-01-17 R/peat6_processing.R

@@ -21,7 +21,7 @@ daily <- peat6_all %>%
             vGPP = mean(wc_gf_var)+mean(er_ANN_var), #error propogation for calculated GPP (NEE-ER)
             ER = mean(er_ANNnight),     #partitioned respiration (umol m-2 s-1)
             vER = mean(er_ANN_var),     #partitioned respiration variance (umol m-2 s-1)^2
-            ET = mean(wq_gf),           #evapotranspiration (umol m-2 s-1)
+            ET = mean(wq_gf),           #evapotranspiration (mmol m-2 s-1)
             q_obs = sum(!is.na(wq)),
             H = mean(H_gf),                    #sensible heat flux (W m-2)
             mGCC = mean(GCC, na.rm=T),   #green index
@@ -46,6 +46,7 @@ daily$mgCH4 <- (daily$mCH4*12.01*3600*24)/1000000 #mg C m-2 d-1
 daily$gCO2 <- (daily$mNEE*12.01*3600*24)/1000000  #g C m-2 d-1
 daily$gER <- (daily$ER*12.01*3600*24)/1000000     #g C m-2 d-1
 daily$gGEP <- (daily$GPP*12.01*3600*24)/1000000   #g C m-2 d-1
+daily$mET <- (daily$ET*18.01528*3600*24)/1000000  #mm H2O d-1
 
 #Annual fluxes from daily fluxes
 yearly <- daily %>%

### 2018-01-18 R/alluvium_processing.R
processing and dataset updates

@@ -3,12 +3,13 @@
 #' Site: Alluvium
 #'
 #' @import dplyr
+#' @import lubridate
 #' @importFrom dplyr "%>%"
 #' @importFrom zoo na.approx
 
 # load eddy flux and met dataset
 load("data/alluvium_all.Rdata")
-alluvium_all$site <- "Alluvium"
+alluvium_all$dday <- floor(alluvium_all$decday)
 
 # create a long-term water temperature measure, as the probes have changed over time
 # when we don't have a 10cm water temp measurement, add 8cm depth in place
@@ -43,12 +44,12 @@ daily <- alluvium_all %>%
             WTD = mean(WT, na.rm=T),           #water table (m from surface)
             Cond = mean(Cond, na.rm=T),        #conductivity (mS)
             t_obs = length(wc_gf),      # total observations in the day
-            month = round(median(month)),
             year = round(median(year))) %>%
   filter(year > 2013 & t_obs == 48) #cut out pre-wetland measures, and incomplete days at edge of time series
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2013-01-01")
+daily$month <- month(daily$datetime)
 daily$mgCH4 <- (daily$mCH4*12.01*3600*24)/1000000 #mg C m-2 d-1
 daily$gCO2 <- (daily$mNEE*12.01*3600*24)/1000000  #g C m-2 d-1
 daily$gER <- (daily$ER*12.01*3600*24)/1000000     #g C m-2 d-1
@@ -69,7 +70,7 @@ yearly <- daily %>%
             Tair = mean(Tair, na.rm=T),
             GCC = mean(mGCC, na.rm=T),
             Days = sum(!is.na(mgCH4))) %>%
-  filter(year < 2017 & Days >= 365) #only keep annual budgets for full years
+  filter(Days >= 365) #only keep annual budgets for full years
 
 #Ecosystem C balance and GHG (CO2eq) balance
 yearly$Cbalance <- yearly$tNEE + yearly$tCH4 #C m-2 yr-1

### 2018-01-18 R/peat19_processing.R

@@ -3,10 +3,13 @@
 #' Site: Peat 19 yr old
 #'
 #' @import dplyr
+#' @import lubridate
 #' @importFrom dplyr "%>%"
 
 # load eddy flux and met dataset
 load("data/peat19_all.Rdata")
+peat19_all$dday <- floor(peat19_all$decday)
+peat19_all$site <- "Old Peat"
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat19_all %>%
@@ -36,12 +39,12 @@ daily <- peat19_all %>%
             WTD = mean(WT, na.rm=T),    #water table (m from surface)
             Cond = mean(conductivity, na.rm=T), #conductivity (mS)
             t_obs = length(wc_gf),      # total observations in the day
-            month = round(median(month)),
             year = round(median(year))) %>%
-  filter(t_obs == 48 & year > 2013)  #remove incomplete days at either end of time series
+  filter(t_obs == 48 & year > 2013)  #remove incomplete days at either end of time series and year with water table drop issues
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2012-01-01")
+daily$month <- month(daily$datetime)
 daily$mgCH4 <- (daily$mCH4*12.01*3600*24)/1000000 #mg C m-2 d-1
 daily$gCO2 <- (daily$mNEE*12.01*3600*24)/1000000  #g C m-2 d-1
 daily$gER <- (daily$ER*12.01*3600*24)/1000000     #g C m-2 d-1
@@ -62,7 +65,7 @@ yearly <- daily %>%
             Tair = mean(Tair, na.rm=T),
             GCC = mean(mGCC, na.rm=T),
             Days = sum(!is.na(mgCH4))) %>%
-  filter(year < 2017 & Days >= 365) #only keep annual budgets for full years
+  filter(Days >= 365) #only keep annual budgets for full years
 
 #Ecosystem C balance and GHG (CO2eq) balance
 yearly$Cbalance <- yearly$tNEE + yearly$tCH4 #C m-2 yr-1

### 2018-01-18 R/peat6_processing.R

@@ -3,10 +3,12 @@
 #' Site: Peat 6 yr old
 #'
 #' @import dplyr
+#' @import lubridate
 #' @importFrom dplyr "%>%"
 
 # load eddy flux and met dataset
 load("data/peat6_all.Rdata")
+peat6_all$dday <- floor(peat6_all$decday)
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat6_all %>%
@@ -36,12 +38,12 @@ daily <- peat6_all %>%
             WTD = mean(WT, na.rm=T),           #water table (m from surface)
             Cond = mean(Cond, na.rm=T),        #conductivity (mS)
             t_obs = length(wc_gf),      # total observations in the day
-            month = round(median(month)),
             year = round(median(year))) %>%
   filter(year > 2010 & t_obs == 48) #cut pre-wetland measures, and incomplete days at ends of time series
 
 #Time and unit conversions
 daily$datetime <- as.POSIXct(daily$dday*86400, origin="2010-01-01")
+daily$month <- month(daily$datetime)
 daily$mgCH4 <- (daily$mCH4*12.01*3600*24)/1000000 #mg C m-2 d-1
 daily$gCO2 <- (daily$mNEE*12.01*3600*24)/1000000  #g C m-2 d-1
 daily$gER <- (daily$ER*12.01*3600*24)/1000000     #g C m-2 d-1
@@ -62,7 +64,7 @@ yearly <- daily %>%
             Tair = mean(Tair, na.rm=T),
             GCC = mean(mGCC, na.rm=T),
             Days = sum(!is.na(mgCH4))) %>%
-  filter(year < 2017 & Days >= 365) #only keep annual budgets for full years
+  filter(Days >= 365) #only keep annual budgets for full years
 
 #Ecosystem C balance and GHG (CO2eq) balance
 yearly$Cbalance <- yearly$tNEE + yearly$tCH4 #C m-2 yr-1

### 2018-01-19 R/soils.R
Lots of revisions & new analysis

@@ -8,9 +8,9 @@
 load("data/soils.Rdata")
 
 #create site variable based on 'Area' site names
-soils$site <- ifelse(soils$Area == "East End", "Peat-Alluvium",
+soils$site <- ifelse(soils$Area == "East End", "Alluvium",
                         ifelse(soils$Area == "West Pond", "Old Peat",
-                               "Young Peat"))
+                               "Peat"))
 
 #What percent of iron is in oxidized form?
 soils$percent_ox <- (soils$FeIII_mg.g/soils$FeT_mg.g)*100
@@ -25,4 +25,4 @@ soils$horizon <- ifelse(soils$Area == "West Pond" & soils$Point == "P1",
                            "Accreted", soils$horizon)
 
 #re-order factors to group peat sites in legend
-soils$site <- factor(soils$site, levels=c("Peat-Alluvium", "Old Peat", "Young Peat"))
+soils$site <- factor(soils$site, levels=c("Alluvium", "Peat", "Old Peat"))

### 2018-01-20 R/peat19_processing.R
Many revisions discussion, analysis, new figure, renaming sites

@@ -9,7 +9,7 @@
 # load eddy flux and met dataset
 load("data/peat19_all.Rdata")
 peat19_all$dday <- floor(peat19_all$decday)
-peat19_all$site <- "Old Peat"
+peat19_all$site <- "Mature"
 
 #Simple average of daily fluxes for gapfilled values
 daily <- peat19_all %>%

### 2018-01-20 R/soils.R

@@ -9,7 +9,7 @@ load("data/soils.Rdata")
 
 #create site variable based on 'Area' site names
 soils$site <- ifelse(soils$Area == "East End", "Alluvium",
-                        ifelse(soils$Area == "West Pond", "Old Peat",
+                        ifelse(soils$Area == "West Pond", "Mature",
                                "Peat"))
 
 #What percent of iron is in oxidized form?

### 2018-01-20 R/alluvium_processing.R
update to NAMESPACE and dependency loads

@@ -3,7 +3,7 @@
 #' Site: Alluvium
 #'
 #' @import dplyr
-#' @import lubridate
+#' @importFrom lubridate month
 #' @importFrom dplyr "%>%"
 #' @importFrom zoo na.approx
 

### 2018-01-20 R/peat19_processing.R

@@ -3,7 +3,7 @@
 #' Site: Peat 19 yr old
 #'
 #' @import dplyr
-#' @import lubridate
+#' @importFrom lubridate month
 #' @importFrom dplyr "%>%"
 
 # load eddy flux and met dataset

### 2018-01-20 R/peat6_processing.R

@@ -3,7 +3,7 @@
 #' Site: Peat 6 yr old
 #'
 #' @import dplyr
-#' @import lubridate
+#' @importFrom lubridate month
 #' @importFrom dplyr "%>%"
 
 # load eddy flux and met dataset

### 2018-01-23 R/Diel_patterns.R
most strucutural revisions

@@ -10,6 +10,8 @@ load("data/peat6_all.Rdata")
 load("data/peat19_all.Rdata")
 load("data/alluvium_all.Rdata")
 
+peat19_all$site <- "Mature"
+
 ## Process each core site into diel values then we will merge them into a single file for visualization
 # diel fluxes from 6yr old peat site
 diel_peat6 <- peat6_all %>%

### 2018-01-23 R/soils.R

@@ -25,4 +25,4 @@ soils$horizon <- ifelse(soils$Area == "West Pond" & soils$Point == "P1",
                            "Accreted", soils$horizon)
 
 #re-order factors to group peat sites in legend
-soils$site <- factor(soils$site, levels=c("Alluvium", "Peat", "Old Peat"))
+soils$site <- factor(soils$site, levels=c("Alluvium", "Peat", "Mature"))

### 2018-02-23 README.Rmd
Readme update

@@
 
-This package was used the generate the manuscript "Effect of soil iron content and sediment accretion on methane fluxes from restored wetlands." by Samuel D.
+This package was used the generate the manuscript "Soil properties and sediment accretion modulate methane fluxes from restored wetlands." by Samuel D.
 Chamberlain et.
 al.
-This was my first attempt at a reproducible research example, and it follows the R package structure adapted from Carl Boettiger's template found here: https://github.com/cboettig/template.
+This follows the R package structure adapted from Carl Boettiger's template found here: https://github.com/cboettig/template.
 Briefly, the /data folder contains soil and half-hourly eddy covariance files used in the analysis, the /R folder contains scripts used to process data, and the /vignettes folder contains the Markdown and bibiography files used to generate the manuscript, as well as two figure images that were not directly reproducible in R.
-Additionally, /man and /test folders are standard in R packages but are not particularly relevant to this manuscript as functions are not introduced in this package.
-They are included anyway to follow convention.
 
-Figure 1 and 7 are not directly reproducible in R, but all other analyses herein are reproducible in this package.
-Figure 1 was generated in ArcMap using the soil series data downloaded from the USDA Web Soil Survey (https://websoilsurvey.sc.egov.usda.gov/), and flux footprints generated from our half-hourly flux data using 2D analytical footprint models described in Detto et al.
-2006.
-Figure 7 was generated using a combined information theory-wavelet time series decomposition using a modification of the MATLAB ProcessNetwork Software found here: https://github.com/samdchamberlain/ProcessNetwork_Software.
+Figure 1 and 4 are not directly reproducible in R, but all other analyses are reproducible in this package.
+Figure 1 was generated in ArcMap using the soil series data downloaded from the USDA Web Soil Survey (https://websoilsurvey.sc.egov.usda.gov/) and eddy covariance flux footprints.
+Figure 4 was generated using a combined information theory-wavelet time series decomposition using a modification of the MATLAB ProcessNetwork Software found here: https://github.com/samdchamberlain/ProcessNetwork_Software.
 All other analyses in this work are reproducible from the 'manuscript.Rmd' file in the /vignettes folder, and running this file will reproduce this manuscript in its entirety.
